%!TEX root = ../dissertation.tex

\chapter{Thesis work plan}
\label{chapter:conclusion}
In order to reach the objectives of this thesis, it is necessary to establish a work order to be carried out. These objectives are listed below.


    
\begin{enumerate}

    \item Draw the hands of vizzy on Syngrasp: Syngrasp \cite{malvezzi2013syngrasp}  is a matlab toolbox that allows custom drawing of robotic hands through their Denavit-Hartenberg parameters.
    
    \item Compute a set of metrics for Vizzy's hand in simulation environment: Syngrasp also allows to compute some metrics for the defined hand. For other metrics, it is necessary to develop some code to compute them.
    
    \item Compute the metrics above on Vizzy's hand: After verifying which are better grasps to grab the object through the calculated metrics in simulation environment, they will be tested on Vizzy. The data from this grasp tests must be collected for future analyze of results. 
    
    \item Analyze and compare results: Here it is verified whether the best grasps calculated in the simulation are successful when implemented in Vizzy's robotic hand. Also, it will be attempted to find out which are the best metrics that will lead to a better grasp.
    
    \item Write the thesis: In the thesis will be described the metrics used, the way in which the position of the hand was obtained through the tactile sensors, and the success rate between the optimum grasp obtained in the simulation environment and those performed by Vizzy's hand.
    
    
\end{enumerate}
